Output Summary

### 2023-04-11 03-post-process/output-plots-children/06-length-based-survival.Rmd
Reorganize length-based output plots
Now in two sections: mean length and length vs. survival relationships

# Length-Based Quantities {.tabset .tabset-dropdown}

## Mean Parr Length vs. Egg Density

```{r}
plot_f = function(j) {

  # obtain posterior samples of total egg abundance scaled to WUL
  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))

  # summarize scaled egg abundance
  E_scaled_mean = post_summ(post_E, ".")["mean",]
  E_scaled_lwr = post_summ(post_E, ".")["2.5%",]
  E_scaled_upr = post_summ(post_E, ".")["97.5%",]

  # create a vector of scaled egg abundances to calculate at
  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)

  # extract posteriors of coefficients
  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)

  # extract posterior summaries of summer length outcomes
  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

  # function to create predicted survival curves for one posterior sample
  pred_fn = function(i) {
    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
    pred_L_Pb
  }

  # calculate predicted survivals and add to posterior samples
  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))

  # extract summarize predicted length
  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))

  plot(1,1, type = "n", 
       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
       xlim = range(0, E_scaled_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)

  # realized pairs
  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, xlab)
mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
```

## Smolt Mean Length {.tabset .tabset-pills}

### "Growth Factor" vs. Parr Mean Length

```{r}
plot_f = function(j) {

  # extract posterior summaries of summer length outcomes
  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

  # extract posterior summaries of growth outcomes
  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

  # create a vector of scaled summer lengths to calculate at
  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]

  # extract posteriors of coefficients
  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)

  # function to create predicted curves for one posterior sample
  pred_fn = function(i) {
    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
    pred_Delta_L_Pb_Mb
  }

  # calculate predicted growth values and add to posterior samples
  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))

  # extract summarize predicted growth
  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
```

### "Growth Factor" Time Series

```{r}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs,
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
```

## Parr $\rightarrow$ Smolt Overwinter Survival vs. Parr Mean Length

@@

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn2)
mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

## Smolt Survival to LGR vs. Smolt Mean Length

```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
plot_fn = function(j, i) {

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
```

>>>>

# Length-Based Survival {.tabset .tabset-pills}

## Parr $\to$ Smolt Overwinter Survival

@@

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn2)
mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

## Smolt Survival to LGR

```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
plot_fn = function(j) {

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Smolt Mean Length (mm)")
mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
```

### 2023-04-11 03-post-process/output-plots.Rmd
Reorganize length-based output plots
Now in two sections: mean length and length vs. survival relationships

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_length_based_values:
    label: "Include Length-Based Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r length-based-values, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_length_based_values}
```

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r mean-length, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_mean_length}
```

```{r length-based-values, child = "output-plots-children/06-length-based-survival.Rmd", eval = params$include_surv_vs_length}
```
